Deeply Virtual Compton Scattering measurement off bound protons

### 2018-08-24 eg6-letters/incoherent/incoherent_prl.tex
update the asymmetry ratio plot in the incoherent paper

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
%\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $x_B$. The black squares are from this 
   work, the green circle is the HERMES measurement 
   \cite{Airapetian:2009cga}. The blue and red curves are results of off-shell 
   calculations \cite{simonetta_2}. The solid and dashed black curves are from 
   on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

>>>>

\begin{figure}[tb]
\centering
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
   work, the green circle is the HERMES measurement \cite{Airapetian:2009cga}.  
   The error bars represent the statistical uncertainties, while the gray bands 
   represent the systematic uncertainties. The blue and red curves are results 
   of off-shell calculations \cite{simonetta_2}. The solid and dashed black 
   curves are from on-shell calculations \cite{Guzey:2008fe}.} 
   \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}
